MacLeish

### 2022-06-06 README.Rmd
added lifecycle badge

[![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)  [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->
